Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-08 exp1/iswc2013.tex
sparql citation a bit on conclusions
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@539 43ef1190-90fd-4dd7-a769-d0121f02b80e

The present experiment is very primitive in its choice of factors, and
we believe that the strategy employed to construct suitable
experiments will be the main determinant for the long-term feasibility
of this direction. One strategy will be to start with broad factors
such as ``Machine'' and refine them with experience. A more difficult
issue is how to address the problem of testing the whole SPARQL
language. We believe that the parameterization work inititated by
\cite{goerlitz2012splodge} with their SPLODGE system is a key
ingredient. They parameterized SPARQL queries in such a way they could
be autogenerated. One suggestion is to parameterize queries based on
the grammar, so that one factor becomes the number of e.g. UNIONs, and
the levels are chosen. One problem one will soon run into is that
parts of the language is recursive, e.g. a GroupGraphPattern can
consist of several GroupGraphPatterns. However, we believe that
pragmatic limits can be set, it is for example not of practical
interest to nest OPTIONALs to any great depth even if it is allowed by
the language.

@@

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{practical,selectivity,federation,benchmarks,optimization,experimentsperformance}

>>>>

The present experiment is very primitive in its choice of factors, and
we believe that the strategy employed to construct suitable
experiments will be the main determinant for the long-term feasibility
of this direction. One strategy will be to start with broad factors
such as ``Machine'' and refine them with experience. A more difficult
issue is how to address the problem of testing the whole SPARQL
language\cite{sparql11query}. We believe that the parameterization work inititated by
\cite{goerlitz2012splodge} with their SPLODGE system is a key
ingredient. They parameterized SPARQL queries in such a way they could
be autogenerated. One suggestion is to parameterize queries based on
the grammar, so that one factor becomes the number of e.g. UNIONs, and
the levels are chosen. One problem one will soon run into is that
parts of the language is recursive, e.g. a GroupGraphPattern can
consist of several GroupGraphPatterns. However, we believe that
pragmatic limits can be set, it is for example not of practical
interest to nest OPTIONALs to any great depth even if it is allowed by
the language.

@@

We saw that while 2 level experiments can perform well in determining
significant effects, they do not necessarily work well to find a
model, as exemplified by failure to identify the probable non-linear
effect of the P-ATA disks. This issue would be fixed by using an
orthogonal array design.

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{practical,selectivity,federation,benchmarks,optimization,experimentsperformance,specs}
